Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-14 robdml.tex
tex

\noindent\textbf{III. Intra-Class Structure.}
%
$L_\text{ICS}$ is independent to HM, but is incompatible with ACT as it does
not create adversarial anchor.
%
Thus, we validate this loss term with HM.
%
{\bf{As shown in \cref{tab:ics} and \cref{fig:icscurve}, $L_\text{ICS}$ consistently
leads to a higher efficiency in gaining higher robustness at a low training
cost, while retaining an acceptable trade-off in R@1.}}

@@

Apart from that, our method HM[$\mathcal{S},g_\mathsf{LGA}$] outperforms the
previous methods in every aspect, as shown in \cref{fig:introplot} for 
example.
%
Although HM[$\mathcal{R},\mathcal{M}$] and HM[$\mathcal{R},g_\mathsf{LGA}$] can reach
a higher ERS, they are excluded from comparison because they induce a
significant performance drop in R@1.

>>>>

\noindent\textbf{III. Intra-Class Structure.}
%
$L_\text{ICS}$ is independent to HM, but is incompatible with ACT as it does
not create adversarial anchor.
%
Thus, we validate this loss term with HM.
%
As shown in \cref{tab:ics} and \cref{fig:icscurve}, $L_\text{ICS}$ consistently
leads to a higher efficiency in gaining higher robustness at a low training
cost, while retaining an acceptable trade-off in R@1.

\noindent\textbf{IV. Summary.}
%
Eventually, HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS overwhelmingly outperforms
the state-of-the-art defense in robustness, training cost, and R@1 
performance, as shown in \cref{fig:introplot}.

@@

Apart from that, our method HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS outperforms the
previous methods in every aspect, as shown in \cref{fig:introplot} for 
example.
%
Although HM[$\mathcal{R},\mathcal{M}$] and HM[$\mathcal{R},g_\mathsf{LGA}$] can reach
a higher ERS, they are excluded from comparison because they induce a
significant performance drop in R@1.
